\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-02-18 papers/itsc_2012/root.tex
Minor revisions and my comments

\author{Dustin Carlino, Mike Depinet, Piyush Khandelwal, and Peter Stone\\
        Department of Computer Science\\
        The University of Texas at Austin\\
        Austin, TX 78712\\
        % TODO mike, what's your utcs unixname?
        {\tt \small\{dcarlino,msdepinet,piyushk,pstone\}@cs.utexas.edu}}

@@

The arrival of driver-less cars presents a number of challenges that need to addressed in the near term. Road infrastructure needs to be updated to better support autonomous vehicles. A number of legal and safety concerns need to be addressed in the context of driver-less cars. Human drivers need new methodologies to interact with autonomous drivers on public roads. At the same time, driver-less cars provide opportunities of solving traffic problems in ways that were never before possible. For instance, autonomous cars can be quickly diverted to make way for emergency vehicles responding to an accident. Even day-to-day traffic issues such as congestion could potentially be greatly reduced by effective management of traffic flow. This work attempts to address some of these problems.

@@

\commentd{terminology is awkward. if we bold-face our notions of edge and vertex
every time we use them, would that better distinguish them from a graph's
verts/edges?}

>>>>

\author{Dustin Carlino, Mike Depinet, Piyush Khandelwal, and Peter Stone\\
        Department of Computer Science\\
        The University of Texas at Austin\\
        Austin, TX 78712\\
        {\tt \small\{dcarlino,msd775,piyushk,pstone\}@cs.utexas.edu}}

@@

The arrival of driver-less cars presents a number of challenges that need to be addressed in the near term. Road infrastructure needs to be updated to better support autonomous vehicles. A number of legal and safety concerns need to be addressed in the context of driver-less cars. Human drivers need new methodologies to interact with autonomous drivers on public roads. At the same time, driver-less cars provide opportunities of solving traffic problems in ways that were never before possible. For instance, autonomous cars can be quickly diverted to make way for emergency vehicles responding to an accident. Even day-to-day traffic issues such as congestion could potentially be greatly reduced by effective management of traffic flow. This work attempts to address some of these problems.

@@

\commentd{terminology is awkward. if we bold-face our notions of edge and vertex
every time we use them, would that better distinguish them from a graph's
verts/edges?}
\commentm{Why don't we limit ourselves to the words used in traffic for our
structures (intersections, roads, lanes, etc.) and use graph-related terms
(edges, vertices) to mean their strict graph theory definitions?  Emphasizing
our structures the first time we use them may be helpful too.}
